\section{Transaction DAGs}
  There exists a genesis transaction that contains all coins to ever exist. This
  transaction is hardcoded in the protocol and is by definition \textit{valid} and
  \textit{trustworthy} for all nodes.
  \begin{center}
    \begin{dot2tex}[outputdir=dot2tex/, file=coinbase]
      \input{src/figures/coinbase.dot}
    \end{dot2tex}
  \end{center}
  All other transactions must have the following attributes to be valid:
  \begin{itemize}
    \item Inputs that correspond to valid unspent outputs (UTXOs) of previous
    transactions.
    \item Outputs that have a total value that is less than or equal to the total value of
      the inputs, with a public key corresponding to each output. Each public key can
      exist only once in the valid and trustworthy DAG of a node\footnote{This is to
      ensure that a transaction input cannot be connected with two different transaction
      outputs. It is not entirely clear that this limitation is necessary though.}.
    \item One signature for each input, made with the private key that corresponds to the
      public key of the corresponding previous output.
  \end{itemize}
  At any point in time, $Alice$ considers a DAG $X$ of transactions as \textit{valid} and
  \textit{trustworthy}. She may be informed by Charlie about the existence another DAG of
  transactions, $Y$. To consider this DAG valid, $Alice$ must verify that
  \begin{itemize}
    \item all the transactions are valid and
    \item all root transactions of $Y$ are connected to UTXOs in $X$.
  \end{itemize}
  We will later see what course of action she is expected to take in case the second
  requirement does not hold.

  For example, let $X$ be:
  \begin{center}
    \begin{dot2tex}[outputdir=dot2tex/, file=basedag]
      \input{src/figures/basedag.dot}
    \end{dot2tex}
  \end{center}
  Then $Alice$ would consider $Y_1$ valid, but $Y_2$ invalid:
  \begin{center}
    \begin{dot2tex}[outputdir=dot2tex/, file=gooddag]
      \input{src/figures/gooddag.dot}
    \end{dot2tex}
  \end{center}
  \begin{center}
    \begin{dot2tex}[outputdir=dot2tex/, file=baddag]
      \input{src/figures/baddag.dot}
    \end{dot2tex}
  \end{center}
  $X$ and $Y_2$ cannot be valid at the same time because there is a conflict regarding
  which private key can spend the output of the transaction $B$. The existence of the two
  versions of the transaction $B$ is proof that $Bob$ attempted to double spend his output
  from transaction $A$. $Alice$ and $Charlie$ just discovered a proof of fraud commited by
  $Bob$ and can use this proof of fraud so that one of the two can keep the coins in the
  transaction DAG and the other can get a refund from the network. Here is where the
  global part of the infrastructure comes into play.
